### 2014-04-17 brains-protocol.tex
Rework substitution detection paragraph, and figure

Let us give an example: say the quotation ``These accusations are false and \textbf{absurd}'' ($q_a$) appears in a blog on January 18, and the slightly different quotation ``These accusations are false and \textbf{incoherent}'' ($q_b$) appears in other blogs twice on the 19th and once on the 20th of January.
If $q_a$ was sufficiently prominent when $q_b$ first appeared, we can safely assume that the first author of $q_b$ on the 19th based himself on $q_a$.
But what about the second occurrence of $q_b$ on the 19th, and the one on the 20th?
Should we consider them to be substitutions based on $q_a$ (i.e. re-creations of $q_b$ by a new instance of the substitution process that brought from $q_a$ to $q_b$ in the first place) or reproductions of the first occurrence of $q_b$?

@@

To settle this question we can model the process as follows: we assume that when a quotation $q$ appears at time $t$, if it is not original (i.e. if not stemming from a source external to the dataset, e.g. initiating a new set of quotations), then it is based solely on the most frequent quotation $q_{max}$ in the preceding period of time $[t - \Delta t ; t]$.
The length $\Delta t$ of that period of time is chosen as a fixed number of days (2 days in the implementation).
If $q$ differs from $q_{max}$ by only one word, as noted above, it is counted as a substitution from $q_{max}$ to $q$.
In any other case, i.e. if $q$ and $q_{max}$ are the same or if $q$ and $q_{max}$ are different in other ways, the occurrence of $q$ is not considered to be an instance of substitution and is discarded.

An example of this detection in a situation akin to the one described above can be seen in Figure \ref{fig:substitution-detection-example}: $q_a$ and $q_b$ differ by only a word, and $q_a$ appears first, once, and so is the most frequent in the beginning.
The first two occurrences of $q_b$ are therefore detected as substitutions stemming from $q_a$.
After a time the situation is reversed and $q_b$ becomes more frequent than $q_a$: in this time frame $q_b$ is thus inaccurately considered as the original quote.
This entails that occurrences of $q_b$ are seen as identical occurrences of the original quote, while occurrences of $q_a$ are detected as substitutions stemming from $q_b$.

>>>>

Let us give an example: say the quotation ``These accusations are false and \textbf{absurd}'' ($q_a$) appears in a blog on January 19, and the slightly different quotation ``These accusations are false and \textbf{incoherent}'' ($q_b$) appears in other blogs on the 21st, 22nd and 23rd of January.
If $q_a$ was sufficiently prominent when $q_b$ first appeared, we can safely assume that the first author of $q_b$ on the 21st based himself on $q_a$ as is shown in the top drawing of Figure~\ref{fig:substitution-detection-example1}.
But what about the second and third occurrences of $q_b$, on the 22nd and 23rd?
Should we consider them to be substitutions based on $q_a$ (i.e. re-creations of $q_b$ by a new instance of the substitution process that brought from $q_a$ to $q_b$ in the first place) or accuratee reproductions of the earlier occurrences of $q_b$ (options shown in Figure~\ref{fig:substitution-detection-example1})?

@@

To settle this question we bin the quote occurrences into fixed \emph{time bags} spanning $\Delta t$ days (2 days in the implementation), each one representing a unit of time evolution
We further assume that when a quotation $q$ appears in time bag $i$, if it is not original (i.e. if not stemming from a source external to the dataset, e.g. initiating a new set of quotations), then it is based solely on the most frequent quotation $q_{max}$ in the preceding time bag ($i - 1$).
If $q$ differs from $q_{max}$ by only one word it is counted as a substitution from $q_{max}$ to~$q$.
In any other case, i.e. if $q$ and $q_{max}$ are the same or if $q$ and $q_{max}$ are different in other ways, the occurrence of $q$ is not considered to be an instance of substitution and is discarded.

This model has two main effects.
First, the binning influences how many times quote occurrences can be counted as substitutions: in the second drawing on Figure~\ref{fig:substitution-detection-example1}, occurrences of $q_b$ on the 21st and 22nd are counted as substitutions, whereas the occurrence on the 23rd is not.
Second, the ``majority'' rule defines how quotes are sourced in substitutions: in the third drawing on Figure~\ref{fig:substitution-detection-example1}, $q_b$ holds the majority and is the considered the basis for the last occurrence of $q_a$, in spite of $q_a$ having appeared earlier at the very beginning (indeed in the situation shown in Figure~\ref{fig:substitution-detection-example1}, this seems the most likely scenario).
